---
title: "Prediction intervals"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Rules

1. You can use any programming language, but the results must be reproducible. 

2. By the deadline, you should send me a **.txt file** (named "[badge number]\_[dataset name].txt") containing the prediction intervals in the format
\begin{verbatim}
5.646867 14.98694
7.825673 17.05896
...
\end{verbatim}
and a **.pdf file** (named "[badge number]\_[dataset name]\_SUPPL.pdf") containing the code to reproduce your results.

3. Deadline: December 10, 2021 h 17:00

# Supplementary code to reproduce the results

```{r}
PATH <- "https://raw.githubusercontent.com/aldosolari/SL3/main/docs/"
train = read.csv2(paste0(PATH,"PI_LOW_train.txt"))
test = read.csv2(paste0(PATH,"PI_LOW_test.txt"))
model = lm( y~. , train )
PI = predict(model, newdata = test, interval = "prediction")[,-1]
head(PI)
# write.table(file="2575_PI_LOW.txt", PI, row.names = FALSE, col.names = FALSE)
```

