---
title: "Statistical Learning III"
subtitle: "Data Analysis"
author: Aldo Solari
output:
  xaringan::moon_reader:
    css: [default, default, rutgers-fonts]
---

```{r startup, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo=T, 
                      eval=T, 
                      message=F, 
                      warning=F, 
                      error=F, 
                      comment=NA)
```


# PI LOW

Simulated data as described in Friedman (1991) and Breiman (1996). 

Inputs are 10 independent variables uniformly distributed on the interval [0,1], only 5 out of these 10 are actually used. 

Outputs are created according to the formula

$$y = 10 \sin(π x_1 x_2) + 20 (x_3 - 0.5)^2 + 10 x_4 + 5 x_5 + e$$

where $e$ is $N(0,1)$.

---

```{r, echo=FALSE}
library(dplyr)
library(mccr)

PATH = "/Volumes/GoogleDrive/My Drive/PHDECOSTAT/XXXIV_CYCLE/SL3/Exam/"
y0 = read.csv2(paste0(PATH,"TRUE/PI_LOW_y0.txt"), header = T)$y0
consegna = list.files(paste0(PATH,"PI_LOW"))

coverage <- vector()
width <- vector()
widthadj <- vector()
for (i in 1:length(consegna)){
  TXT = consegna[i]
  out = read.table(paste0(PATH,"PI_LOW/",TXT))
  coverage[i] = mean(out$V1 <= y0 & y0 <= out$V2)
  grid = seq(0,10,length.out = 500)
  C = grid[which.max(sapply(grid, function(c) mean(out$V1 - c <= y0 & y0 <= out$V2 + c) ) >=.9 )]
  width[i] = mean(out$V2 - out$V1)
  widthadj[i] = width[i] + 4*C
}
res = data.frame(id=consegna, coverage, width, widthadj)
#res$score = round( ( res$widthadj - max(res$widthadj) ) / ( min(res$widthadj) - max(res$widthadj)  ), 2)
res %>% arrange( widthadj)

#A = res$score
```

---

# PI HIGH

Simulated data as described in Sesia et al.

$X \sim U([0,1]^d)$ and
$$Y = f(\beta' X) + \epsilon \sqrt{1+(\beta'X)^2}$$
where $f(x) = 2\sin(\pi x)$, $\beta' = (1,1,1,1,1,0,\ldots,0)$ and $\epsilon$ is independent standard Gaussian noise.

The expected width of the oracle prediction bands is $\approx 8.91$

---

```{r, echo=FALSE}
PATH = "/Volumes/GoogleDrive/My Drive/PHDECOSTAT/XXXIV_CYCLE/SL3/Exam/"
y0 = read.csv2(paste0(PATH,"TRUE/PI_HIGH_y0.txt"), header = T)$V1
consegna = list.files(paste0(PATH,"PI_HIGH"))

coverage <- vector()
width <- vector()
widthadj <- vector()
for (i in 1:length(consegna)){
  TXT = consegna[i]
  out = read.table(paste0(PATH,"PI_HIGH/",TXT))
  coverage[i] = mean(out$V1 <= y0 & y0 <= out$V2)
  grid = seq(0,10,length.out = 500)
  C = grid[which.max(sapply(grid, function(c) mean(out$V1 - c <= y0 & y0 <= out$V2 + c) ) >=.9 )]
  width[i] = mean(out$V2 - out$V1)
  widthadj[i] = width[i] + 4*C
}
res = data.frame(id=consegna, coverage, width, widthadj)
#res$score = round( ( res$widthadj - max(res$widthadj) ) / ( min(res$widthadj) - max(res$widthadj)  ),2)
res %>% arrange( widthadj)

#B = res$score
```

---

# VS

Data from Stanford HIV Drug Resistance Database

96 relevant variables

---

```{r, echo=FALSE}

PATH = "/Volumes/GoogleDrive/My Drive/PHDECOSTAT/XXXIV_CYCLE/SL3/Exam/"
S = read.csv2(paste0(PATH,"TRUE/trueS.txt"), header = T)$x
consegna = list.files(paste0(PATH,"VS"))
TDP <- vector()
FDR <- vector()
MCC <- vector()
act = (1:201 %in% S)*1
SIZE <- vector()
for (i in 1:length(consegna)){
  TXT = consegna[i]
  Shat = read.table(paste0(PATH,"VS/",TXT))$V1
  SIZE[i] <- length(Shat)
  pred = (1:201 %in% Shat)*1
  FDR[i] <- (length(Shat) - sum(Shat %in% S))/max(1,length(Shat))
  TDP[i] <- (sum(Shat %in% S))/length(S)
  MCC[i] <- mccr(act,pred)
}
res = data.frame(id=consegna, SIZE, FDR, TDP, MCC)
#res$score = round( ( res$MCC - min(res$MCC) ) / ( max(res$MCC) - min(res$MCC)  ) , 2)
res %>% arrange(desc(MCC))

#C = res$score
```

<!-- # SCORE -->

<!-- ```{r, echo=FALSE} -->
<!-- res$tot = round( ( (A+B+C) /3 ) * 50 )  -->
<!-- res %>% select(id,tot) %>% arrange(desc(tot)) -->
<!-- ``` -->

